### 2020-09-24 LaTeX/sections/paper.tex
DONE!

\paragraph{Other Academic Literature.} There are numerous industry projects on blockchain-based exchanges and order books but most of the academic literature is on topics that are related but tangential to the mechanics of trade execution. Early literature considered trade execution under encryption (\ie dark markets)~\cite{TP07,YSLT10,TW12}. A number of projects consider structuring futures and derivatives in smart contracts---Velocity ~\cite{eskandari2017feasibility}, Findel ~\cite{biryukov2017findel}, FuturesMex~\cite{massacci2018futuresmex}---but once issued, the derivative can be traded using exchanges. Atomic swaps (\ie payment vs delivery) are necessary for settling trades and some general approaches include Arwen~\cite{heilman2020arwen} and Tesseract~\cite{bentov2017tesseract}.

>>>>

\paragraph{Other Academic Literature.} There are numerous industry projects on blockchain-based exchanges and order books but most of the academic literature is on topics that are related but tangential to the mechanics of trade execution. Early (and some recent) literature consider trade execution under encryption (\ie dark markets) for securities~\cite{TP07,YSLT10,TW12,cartlidge2019mpc} and futures~\cite{massacci2018futuresmex}. A number of projects consider structuring derivatives in smart contracts---Velocity ~\cite{eskandari2017feasibility}, Findel ~\cite{biryukov2017findel}---but once issued, the derivative can be traded using exchanges. Atomic swaps (\ie payment vs delivery) are necessary for settling trades and some general approaches include Arwen~\cite{heilman2020arwen} and Tesseract~\cite{bentov2017tesseract}.
